##Analysis

###Ridge Regression (RR)
We fit the training data using 10-fold cross-validation with many different values for the $\lambda$ parameter of ridge regression, from $10^{10}$ to $10^{-10}$. Figure 3 is the plot of Mean Square Error (MSE) and $\lambda$ values during cross-validation. We choose the $\lambda$ with the smallest associated error, which is $`r ridge.best.lambda`$. We the calculate the MSE of the model with this $\lambda$ using the test set, which is `r ridge.error`.

###Lasso Regression (LR)
Like above, we use 10-fold cross-validation to fit lasso models with $\lambda$ values from $10^{10}$ to $10^{-10}$ with the training data. Figure 4 is the plot of MSE against the tuning parameter values. The min error came from the $\lambda$ of $`r lasso.best.lambda`$, producing a MSE on the test set of `r lasso.error`.

###Principal Components Regression (PCR)
We fit the training data using cross-validation on the numbers of principal components. Figure 5 is the plot of Mean Square Error (MSE) of the predictions and number of components during cross-validation. Again, we choose the best number of components (resulting in minimum error), which is `r pcr.best.ncomp`. We then calculated the MSE of the `r pcr.best.ncomp`-component model using the test set, which turned out to be `r pcr.error`. 

###Partial Least square Regression (PLSR)
Again, we fit the training data using cross-validation on the numbers of components. Figure 6 is the plot of the MSE and number of components during cross-validation. The minimum error was achieved by `r plsr.best.ncomp` components. This resulted in a MSE `r plsr.error` on the test set.

```{r, fig.height = 2.5, fig.align = 'center', fig.cap = "Ridge: MSE vs Shrinkage Param"}
ridge.cv <- readPNG("../../images/ridge-scatterplot.png")
grid.raster(ridge.cv)
```
```{r, fig.height = 2.5, fig.align = 'center', fig.cap = "Lasso: MSE vs Shrinkage Param"}
lasso.cv <- readPNG("../../images/lasso-scatterplot.png")
grid.raster(lasso.cv)
```
```{r fig.width = 2.5, fig.align = 'center', fig.cap = "MSE vs Num Components"}
plsr.cv <- readPNG("../../images/plsr-scatterplot.png")
grid.raster(plsr.cv)
```
```{r fig.width = 2.5, fig.align = 'center', fig.cap = "MSE vs Num Components"}
pcr.cv <- readPNG("../../images/pcr-scatterplot.png")
grid.raster(pcr.cv)
```

---
